---
title: "Introduction"
author: "Huandong"
date: "2022-12-25"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

In most of the functions, the function paramaters follow the pattern of dataset, response variable, factor 1, factor 2, factor 3. The function details can be check typing *?[function_name]* in the R Console. If you have less than the paramaters listed here, in most cases you can simply ignore the extra ones and the function has the mechanisms to deal with these issues.  


## An example using dataset Towels2

```{r}
library(easyExp)
```

#### A box plot to check the equal variances assumption in ANOVA

```{r}
var_boxplot(Towels2, LogStrength, Brand, Water)
```

#### A scatterplot to check the equal variances assumption in ANOVA

```{r}
var_scatterplot(Towels2, LogStrength, Brand, Water)
```

#### An interactive table to show variances of different groups

```{r}
var_table(Towels2, LogStrength, Brand, Water)
```

You can sort the GroupVariance or other columns by clicking the column name.  


#### A qqplot and a histogram for residuals

```{r}
normal_err(Towels2, LogStrength, Brand, Water, interaction = TRUE)

# Alternatively, you can use residuals as the function input in cases like split-plot designs.
aov1 = aov(LogStrength~Brand*Water, Towels2)
# normal_err(aov1$residuals)
```

#### Residual vs fit and residual vs order plots

```{r}
iid(Towels2, aov1)
```

#### ANOVA Table

```{r}
summary(aov1)
```

#### Main Effect Plots

```{r, message = FALSE}
main_plot(Towels2, LogStrength, Brand, Water)
```


If you are only interested in one treatment (or you have a 3-way ANOVA), you can simply add (or reduce) parameters in the function inputs.  


#### Interaction Effect Plot

```{r}
interaction_plot(Towels2, LogStrength, Brand, Water)
```
